---
title: "Cpts575 Hw3"
author: "Mengxiao"
output: pdf_document
---
# Part 1
```{r}
library(dplyr)
#msleep = read.csv('https://scads.eecs.wsu.edu/wp-content/uploads/2017/10/msleep_ggplot2.csv')
msleep = read.csv('msleep_ggplot2.csv')
#heads = head(select(msleep, contains('sleep')))
msleep %>%
    select(contains('sleep'))%>%
    head()
```
## a.
```{r}
#count_numbers = count(filter(msleep, bodywt<50, sleep_total>16))
msleep %>%
    filter(bodywt<50, sleep_total>16) %>%
    count()
```
## b.
```{r}
msleep %>%
    select(name, sleep_total, bodywt) %>%
    arrange(desc=msleep$sleep_total) %>%
    top_n(5)
```
## c.
```{r, results="hide"}
msleep = msleep %>%
    mutate(wt_ratio=brainwt/bodywt,
           rem_ratio=sleep_rem/sleep_total)
```
## d.
```{r}
order_sum = data.frame(
    msleep %>%
        group_by(order)%>%
        summarise(avg=mean(sleep_total),
                  max=max(sleep_total),
                  min=min(sleep_total))
    )
order_sum
```
## e.
```{r}
#mutate(msleep, avg_ratio=order_sum[order_sum$order == order,]$avg)
head(msleep)
msleep_copy2 = data.frame(
    msleep %>%
        group_by(order) %>%
        mutate(brainwt)
                          )
```



# Part 2
```{r}
library(tidyr)
head(who)
```
```{r}
mywho = who %>%
    gather(key, value, new_sp_m014:newrel_f65, na.rm = TRUE) %>%
    mutate(key = stringr::str_replace(key, "newrel", "new_rel")) %>%
    separate(key, c("new", "var", "sexage")) %>%
    select(-new, -iso2, -iso3) %>%
    separate(sexage, c("sex", "age"), sep = 1)
head(mywho)

```
## a.
This line tries to replace all the strings name "newrel" to "new_rel". So it tidy the key name of the data.
If I skip this line, we will have one more key called "newrel" and it's data cannot be select when we use the key "new_rel".


## b.
```{r}
unremoved = who %>%
    gather(new_sp_m014:newrel_f65, key="key", value="cases")
Delete_Number = nrow(unremoved) - nrow(mywho)
Delete_Number
```

## c.
1. Explicit missing value means the data is 'NA', 'NAN' or some other Null value.
2. Implicit missing value means the data is just doesn't apear on the table.
From the data we can find that the data after tidy is begin from 1997, but it was begin from 1980. The data between 1980 and 1997 is missing.

## d.
```{r}
mywho2 = mywho %>%
    select(country, year, var, sex, age, value)
```
I think the 'age' should change it's type to 'int', since ages are all int numbers.

## e.
In my opinion, gather is the operation that would help people focus on the characteristics of one or some typical object.
For example, when we have the data of a lot of cars, when we want to compare the details of two cars, then we can gather two cars.
Also, spread do the similar things as gather, but it would catch the different objects' one or some typical characteristics, then
compare the characteristics of different object to know the difference between different unities.

## f.
```{r}
mywho3 <- mywho %>%
    group_by(year) %>%
    summarise(value=sum(value))
plot(mywho3)
c(mywho3['year'])
```
From this scatter I can know the amount of cases is increasing from 1995, but is decrese in the 2013.
I want to know whether the cases decrease with the development of the modern medicine.

## g.
```{r}
siteDemo <- data.frame(Site = c("facebook", "myspace", "snapchat", "twitter"),
                       U30.F = c(32, 1, 6, 17),
                       U30.M = c(31, 5, 4, 23),
                       O30.F = c(60, 3, 3, 12),
                       O30.M = c(58, 6, 2, 17))
siteDemo_new <- siteDemo %>%
    gather('U30.F', 'U30.M', 'O30.F', 'O30.M', key="AGG", value = "Count")
siteDemo_new
siteDemo_new <- siteDemo_new %>%
    separate('AGG', into = c("AgeGroup", "Gender"))
siteDemo_new
```

