---
title: "CptS575 Hw2"
author: "Mengxiao"
output: pdf_document
---

# Part 1

## a. Read the data into R

```{r}
data = read.csv('https://scads.eecs.wsu.edu/wp-content/uploads/2017/09/College.csv')
```

## b. Find the median cost of books

```{r}
books_median = median(data['Books'][, 1])
```

```{r echo=FALSE}
books_median
```

## c. Produce a scatterplot to show the relationship between the cost of books and Top 10 percent students.

```{r}
plot(x = data$Books,
     y = data$Top10perc,
     xlab = "Cost of books",
     ylab = "Top 10 percent",
     main = "Relationship between cost of books and top 10 percent"
     )
```

## d. Produce a histogram showing the overall enrollment numbers for both public and private schools.

```{r}
OverallEnroll <- c(sum(data[data$Private == 'No',]$P.Undergrad)
                   +sum(data[data$Private == 'No',]$F.Undergrad),
                   sum(data[data$Private == 'Yes',]$P.Undergrad)
                   +sum(data[data$Private == 'Yes',]$F.Undergrad))
hist(OverallEnroll, main = "Overall enrollment for both public and private school",
     xlab = "School", ylab = "Enrollment number", col=c("aquamarine3", "coral"),
    )
```

## e. Seperate the schools to two parts, top and ntop(not top)

```{r}
top <- sum(data[data$Top25perc>50,]$Accept)/sum(data[data$Top25perc>50,]$Apps)
ntop<- sum(data[data$Top25perc<=50,]$Accept)/sum(data[data$Top25perc<=50,]$Apps)
barplot(matrix(c(top, ntop)), ylab="Acceptance rate", xlab="School", col=c("aquamarine3", "coral"),
    main="The Acceptance rate of top and not top schools", beside=TRUE, width=0.2,
    names.arg = c("TOP", "NTOP"))
#legend("topleft", legend=c("TOP","NTOP"), fill=c("aquamarine3", "coral"))
```

## f. Produce two new plots.

#### 1. I want to explore the relationship between cost of Rooms and Top 10 students percentage.

```{r}
plot(x = data$Room.Board,
     y = data$Top10perc,
     xlab = "Cost of Rooms",
     ylab = "Top 10 students percent",
     main = "The relationship between cost of Rooms and Top 10 students percent")
```

#### 2. I want to build a pie chart to show the proportion of private and public schools.

```{r}
school_public <- length(data[data$Private == 'Yes',]$Private)
school_private<- length(data[data$Private == 'No', ]$Private)
pie(c(school_public, school_private),
    labels = c("Private", "Public"))
```

# Part 2
```{r}
data2 = read.csv("https://scads.eecs.wsu.edu/wp-content/uploads/2017/09/Auto.csv")
```

