---
title: "Cpts575 Hw4"
author: "Mengxiao"
output: pdf_document
---
# Part 1
```{r}
library(dplyr)
library(graphics)
Auto = read.csv("https://scads.eecs.wsu.edu/wp-content/uploads/2017/09/Auto.csv", na.string = '?')
Auto = na.omit(Auto)
#Auto = Auto[Auto$horsepower != '?',] #Moving out the missing data
```
##  a. Produce a scatterplot matrix
```{r}
pairs(Auto)
```

##  b. Compute the matrix of correlations.
```{r}
Auto2 = Auto %>% select(-name)
cor(Auto2)
```

##  c. Perform a multiple linear regression.
```{r}
lr = lm(mpg~., data = Auto2)
summary(lr)
```
### i. I think the 'origin' and 'year' are the most significant, since their absolute estimate of coefficients are the highest two.
### ii. Means when the value of displacement increase 1%, the mpg will increase 0.019896%.

##  d. Produce diagnostic plots of the linear regression fit.
```{r}
plot(lr)
```
#### The residual plots looks good, but still have some outliers.
#### Yes, it identifies some unusually outliers

##  e.


# Part 2
```{r}
library(MASS)
head(Boston)
```
##  a.
```{r echo=FALSE}

```
