\documentclass[12pt]{article}
\author{Mengxiao}
    \title{Math553}
    \usepackage{graphicx}
\begin{document}
    \maketitle
    \pagebreak
    \section{Abstract}
    \section{Introduction}
        \subsection{Konigsberg seven bridge problem}
        \subsection{The problem}
            I want to travel to Canc\'un this winter vacation, but it is really
            an expensive trip, so I hope to solve money. But how can I save money
            in a trip? What I know is that, I want to go Canc\'un, and I am living
            in Pullman now. So my start point is Pullman, WA. And the end point is
            Canc\'un. Also, if I need to spend so much money to fly to Canc\'un,
            why not travel to some other cities near Canc\'un? So I also want to
            go to the Guanajuanto, M\'erida and Mexico City, these are also really
            beautiful or interesting viewpoints. And finally, I still need to go
            back to Pullman for my next semester's study. It really looks like
            a weighted undirected graph, so I think maybe I can save money with
            the knowledge learn in Graph Theory this semester.
    \section{What is Travelling Salesman Problem}
        Travelling Salesman Problem, also called TSP. It is trying to solve
        the problem that there is a salesman that want to travel around the
        cities and sale his freights. Unfortunately, he need to spend money
        or time on the way between cities. So, how to use the shortest path
        to travel around these cities is the main problem. The TSP is like
        the minimum connector problem but the salesman want to go back home
        at the end.\cite{travellingsalesmanproblem}\\
        According to the situation that the cost travel from $A$ to $B$ is not
        equal to travel from $B$ to $A$, what we talk about is the asymmetric
        travelling salesman problem (aTSP) here. \\
        aTSP: Let $V={v_1,\cdots\cdots,v_n}$ be a set of cities, $A={(r,s):r,s\inV}$
        be the edge set, and $d_{rs}\neqd_{sr}$ be the cost measure associated
        with edge $(r,s)\in A$.\cite{matai2010traveling}\\
        The aTSP is the problem that we need to find a minimal length closed tour
        that visits each city once. In my case, cities $v_i\in V$ are given and $d_{rs}$
        is the cost I will build with the fee of flight and time spend, then
        we will have a typical aTSP.
    \section{How to transform the real-world problem}
        Now, since I want to solve my save money problem, I need to collect the data
        at first. I need to know hwo much should I pay for the flight around these
        cities, or where I want to go don't havev ariport and I need to try some
        other ways. Then, I need to transform these data to a mathmatical model,
        which will let me can use mathmatical ways to solve them. So, I started to
        check the data of fees. However, it's really hard to confirm the fees spend
        one the way. For example, if I just search the way from Pullman to Canc\'un,
        I can get the flight from Pullman to Seattle, and then from Seattle to Canc\'un.
        But I know I can drive to Seattle, and the flight from Seattle to Canc\'un may
        be cheaper than the first choice. Also, what if I try to fly from Lewiston to
        the Canc\'un? It may have some other situation. So I need to mkae some
        rules for the transform form real-world problem to mathmatical models. \\
        The formula I build at first for the way cost is:
        $$C=f+T_1(t)+T_2(s)+e$$
        In this formula,
        $C$ means the total cost of the way.
        $t$ means the time used on the flight.
        $T_1$ is a transformation function that change the time for flight to a score,
        this transformation function can be really personal like if I just want to let
        it be a easy problem and don't care about the difference about long time flight
        and short time flight, then I can set it like a first-order linear function. But
        if I can only bear short time flight and cannot bear to sit for too long, it can
        be a quadratic function or even exponential function. And I want to set it like
        $s$ is the number of transit station in such flight.
        $T_2$ is a transformation function that change the number of transit station to
        a score, it is also really personal. And I want to set it like $50s$ here,
        since I think the time I spend on one transit station is equal to 50 dollars.

        \\I will all use the air tickets data on December 16, 2019. If people want to
        use it on the real problem, they just need to calculate the day they will start
        travel and compute the day they travl between these cities and then check
        the tickets of flight.
    \section{How to solve mathematical model}
    \section{How to extend to this model}
        Since I don't have enough time for build this model and test it, it looks really
        simple. But I think this can be used for people who want to travel to some place,
        and want to save time and money at the same time. I will adjustment the parameter
        of the formula more carefully and think about more factors like the security issue,
        the time limited for the trip and the limitaion of total spend, and finally expand
        it to a more complete combinatorial optimization problem. Also, I can write the
        code for calculate it automatically. And use some ways like Python Spider(a kind
        of program that can catch the data from the website automatically), to catch
        the flight information and clean them as the data used in my formula. I hope it
        can be helpful for people who like traveling.
\end{document}

