\documentclass[12pt]{article}
\author{Mengxiao}
	\title{Cpt575\_SurveyPaper}
	\usepackage{graphicx}
\begin{document}
	\maketitle
	\pagebreak
    \section{Abstract}
        With the development of Artificial Intelligence, various of video games also
        attract a lot of people. This article introduces the application of Artificial
        Intelligence technology in defferent aspects of video games like intelligent virtual
        game roles and the development and promotion of games. And finally discuss the future
        of the application of AI on video games, put forward some direction of the development.
	\section{Introduction}
        Aritificial Intelligence is a kind of technology that can help machine to think or
        act like human. It tells machines how to analyze situations and make corresponding
        actions. In the past, it learn models from developers' codes, what model people write
        down is the behavior it will take. But nowadays, with the appearence of Data Science, it
        start learn models and experience from data. People don't need to enter fixed behavior
        pattern anymore, which make machines more human and rational.\\
        
        Video games, a kind of game that has attracted countless people since its birth. It depends
        on digital technology and equipments, so AI has a very close relationship with it. From
        its development method, game construction to planning and promotion, also includes the
        basic technology like Virtual Reality, all of these fields are using Artificial Intelligence
        technology and Data Science.
    \section{Development Progress}
        \subsection{What it used to be}
            In the 1980s, the appearence of "Pac-Man" and "Half-Life" set off a frenzy among players.
            But at that time, Artificial Intelligence was not strong enough, so what the game roles
            in "Half-Life" are really simple. It like a single relfection machine that when facing
            with a situation, it will check the if-then rules writen by developers an do the reaction
            according to the if-then rules. So, it looks like a gear, if we don't touch or move it,
            it will not act. These game roles do not have any complex action and only have really
            easy mode of action, it will let players feel so boring. Since when people keep playing
            they will find the game stay the same as before. It also bother the game developers,
            because if they want to let the game to be diversification, they need spend a lot of
            time to enter the reaction rules for the game roles, but it just slows down the players'
            boredom, it does not solve the problem.
        \subsection{The main application nowadays}
            However, the AI technology in video games has become quite developed and has been used
            to a lot of different fields. The most significant difference from the past is that the
            sometimes the virtual game roles are more powerful than humans.\\
            
            Another application is on the development of the cheating detection mechanism. Cheating
            is really an abomination that most of the players hate these cheating man. If all of
            the cheating in video games can be identified, most of the FPS games will save many
            disappointed players. This is reflected in many of my friends. I used to paly PUBG,
            a famous video game, but there are too many cheaters in this game. With the accumulation
            of disappointment, my friends and I eventually abandoned this game, although it is
            really interesting.\\
            
            The third application is in game design and operation. There are so many games nowadays
            and how to make their comanies' games stand out become a severe problem to the game
            developers and operators. The appearence of Data Science has been a big boost. They
            used to use traditional business analysis before, but sometimes it's hard to know what
            can really decide the sales. But Data Science make it be possible for these companies.
            The model from the data can help companies know how to design games that can make
            players keep interested and participating in the games. Also, Artificial Intelligence
            can help game companies know how to design the advertisement and put in them$.^{[1]}$
        \subsection{Why would have such improvement}
            What let human can build such powerful robot now? The development of devices is one of the
            most important reason, because now we have larger memory and faster operators, which
            help our robots can do more things than before. However, another one reason is that
            now we have Data Science, with Data Science, we have ability to analyze the large scale
            data, which contains a lot of information we cannot use before. Also, we can get some
            new models by algorithms.
    \section{In Adversarial Game}
        \subsection{Act as a real human}
            If the game roles looks like a real human, or it can chat with you activly and shows its
            happiness, sadness or angry, will people wrongly assume they are real human? Although it
            sounds ridiculous, but it has truly happened. Robots are able to analyze people's emotion
            from their sentences, they can know whether you are happy or not, whether you are sad or
            not, which can really help robots to build emotion and have compassion and empathy. With
            compassion and empathy, these game roles can easily build a close relationship with gamers
            and let gamers love the game and feel it like in a real world. Also, sometimes the machine
            is even better than human, because they will always care about users' emotion, they are
            really selfless and would not blame players. With such empathy, players will feel the
            game roles are really nice and friendly. Whatever they believe this is just robot or not,
            they will try to express themselves and soon build a good relationship atmosphere in the
            game.\\
            
            Also, act as a real human means these robots can help you in the game like a player.
            Sometimes, people are busy with their own jobs and will let someone play the game lonely.
            But there are some games that really need players' teamwork, like "League of legends".
            At that time, robots can replace players to play with those lonely players. It is really
            a good development of the application of AI on video games.
        \subsection{Analysis what is the goal of players}
            When the game developers design the games, one of the most important questions is that
            what makes people love this game? What can make different people all feel interested? It
            is really a hard question, because nowadays we have seven billion people, and all people are
            unique individuals with different preferences, different backgrounds and different purposes
            when playing the game. The Data Science help people to be a fantastic game designers now.
            With study on the data from game players, researchers find that there are four main types
            of players: superachievers, mastery-only, performance-only, and non-achievers. Also,
            gender and gaming frequency are significantly related to gamaing achievement goals.
            There exists a motivation called "mastery goals", which will let people strive to be
            better in the game. Another motivation called "performance goals", which will let people
            try to do better than others, but it may have back action. The reward system orachievement
            system in the game let people with these two motivation can play really happy, because
            they can get honor, get points, get rewards, get the feeling of leader, get the feeling
            of needed.\\

            People with "performance goals" like to fight with other people, they like the feeling
            of better than other people, they like to show their ability and really confident. To
            attract these people, the game designers will provide some battleground for players to
            play against each other, or set some unique goals or pets that only one or small quantity
            of players can achieve these goals or catch these pets. With more comparison scenarios,
            people with "performance goals" will be really excited and will fight for the higher goals.
            Sometimes we call such way "PVP", if players need to battle with each other and like a
            game game.\\

            People with "mastery goals" like to learn from the failure, they are interested in
            developing their competence instead of fight against other people. So they always ignore
            the part that should battle with real human, they like to collect more things, make
            themselvers better and pass through one and another one difficult levels. Also, some of
            these players like to have a team work, because people can do more things when they are
            in a team. Mutual benefit is what they like most, instead of zero-sum game. Sometimes we
            call these people "PVE players".
            [3]
        \subsection{Defeat the top game player}
            There is a virtual palyer built by deep learning, called "AlphaStar", it
            has defeated some of the top players in a human way$.^{[2]}$ It is a new robot build by machine
            learning like "AlphoGo", but it do not know how to play Go, it can play
            "StarCraft II", a really complex real-time strategy adversarial game. Which is not
            possible with the single if-then reflection rules before, because this game has too
            many status that even more than Go game. The state space of Go is about $10^{170}$ and
            the state space of "StarCraft II" may have $10^{1685}$. It is far more beyond what
            human can totally think about. Also, it is an incomplete information game, what we should
            consider is almost all of these state every second. But now we can done this. With the help
            of Data Science, we can analyze what these top players always do in such situation or in
            such time, and then let computer understand these model that come from data. Soon, the
            game robots will know what should they do now. Also, since computers and algorithms are
            absolutely rational, these robots can handle the game better than people, they seldom
            make mistakes. But they are still have defect that they are always try to do things
            with the best way and get the best reward, sometimes it can be predict by human and they
            are unfamiliar with deception. If players know it is just a robot and try to make some
            illusions, this robot will no longer control the game.
    \section{In Checking Cheaters}
        \subsection{Really a struggle}
            Although cheating is really hateful, but those game developers still don't have effective
            ways to check and ban cheaters.
        \subsection{What can be done is not possible before}
    \section{In Game operation and Promotion}
        \subsection{What makes people want to play a game}
            [3]
        \subsection{What let the game make money}
    \section{In the future}
        \subsection{Used in game roles}
        \subsection{Used in gaming device}
        \subsection{Used in checking cheater}
    \section{In conclusion}
    \pagebreak
    \section{Reference}
\end{document}

%[1]
%[2]
%[3]Carrie Heeter, Yu-Hao Lee, Ben Medler, and Brian Magerko. 2011. Beyond player types: gaming achievement goal. In ACM SIGGRAPH 2011 Game Papers (SIGGRAPH '11). ACM, New York, NY, USA, Article 7, 5 pages. DOI: https://doi.org/10.1145/2037692.2037701
%[4]
